Radio Telescope Observations Of The April 8, 2024 Total Solar Eclipse At 1420MHz.

### 2025-02-28 sections/introduction.tex
Replace bullet list in Introduction with sentences. Improved paragraph flow.

Our goal with this project is to determine the size of the radio solar disk by using observations during the April 8th, 2024 Total Solar Eclipse.
This eclipse gave us a unique opportunity to observe the outer atmosphere of the sun without overwhelming our ground-based radio telescope.
To accomplish this, we need to determine how much of the solar disk is obscured by the moon during totality in both the optical and radio wavelengths.
We have only one source of radio lightcurve data: UCA's 2.3 meter radio telescope.
To verify these results, we have multiple sources of optical lightcurve data:
\begin{itemize}
    \item Livestream from the UCA Observatory
    \item Broad-spectrum light sensor pointed at the sky, also at UCA
    \item Theoretical lightcurve generated by Stellarium
\end{itemize}% I don't like how much space there is between bullets

>>>>

Our goal with this project is to determine the size of the radio solar disk by using observations during the April 8th, 2024 Total Solar Eclipse.
This eclipse gave us a unique opportunity to observe the outer atmosphere of the sun without overwhelming our ground-based radio telescope.
To accomplish this, we need to determine how much of the solar disk is obscured by the moon during totality in both the optical and radio wavelengths.
We have only one source of radio lightcurve data: UCA's 2.3 meter radio telescope.
To verify these results, we have multiple sources of optical lightcurve data: a livestream from the UCA Observatory, a broad-spectrum light sensor pointed at the sky, and a theoretical lightcurve generated by the software Stellarium.
Using these data, we can compare the optical and radio lightcurves to determine the relative size of the radio solar disk.
